Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-08-12 2_SSL_NE/article/article_main.tex
added edits

This research was supported by the grant from the Alfred P. Sloan Foundation titled \textit{“What factors drive innovation in energy technologies? The role of technology spillovers and government investment”}. Michael Weinold gratefully acknowledges support from the Swiss Study Foundation. The authors thank Venkatesh Narayanamurti, Gabriel Chan, Anna Goldstein, Didier Sornette, and participants of the SPIE West 2021 Conference and C-EENRG Seminar Series of the University of Cambridge for many helpful discussions and feedback. The authors further express their gratitude to all interviewees for their willingness to participate in this study and share their insights.

Additional context and governing equations of metrics used to quantify progress in solid-state lighting, including the constituent sub-efficiencies of overall lamp efficiency. Detailed description of the multi-method approach used, including the systematic literature review, semi-structured interviews, the manufacturing cost model and performance calculations. Methodological details on dis-aggregation of the contribution of variables to overall lamp efficiency. Additional results, including a breakdown of manufacturing cost and a detailed description of the technology spillovers in phosphor materials for light down-conversion. Complete list of sources for Figures \ref{fgr:history_efficacy} and \ref{fgr:chip_architecture_overview}.

>>>>

\section{Methods}

\subsection{Multi-Method Approach}

\section{Acknowledgements}

This research was supported by the grant from the Alfred P. Sloan Foundation titled “What factors drive innovation in energy technologies? The role of technology spillovers and government investment”. Michael Weinold gratefully acknowledges support from the Swiss Study Foundation. The authors thank Venkatesh Narayanamurti, Gabriel Chan, Anna Goldstein, Didier Sornette, and participants of the SPIE West 2021 Conference and CEENRG Seminar Series of the University of Cambridge for many helpful discussions and feedback. The authors further express their deepest gratitude to all interviewees for their willingness to participate in this study and share their insights.
